00:00:01 Interviewer
OK, keep tracking too with Interviewee 3 on the 1st of December 2022, ethics forms have been signed.
00:00:14 Interviewer
For recording, right? OK. So like I said just now can I go through four different parts, OK, current state analysis. Any suggestions you have an Apple prototypes in the demos.
00:00:28 Interviewer
With your work in RST with me, what are your kind of opinions on the current state of the server room so C30C?
00:00:36 Interviewer
36 movies.
00:00:36 Interviewee 3
C30C36 and C51.
00:00:39 Interviewee 3
Yeah, basically, I think the biggest problem is.
00:00:43 Interviewee 3
And the every every staff in the server room are on tracked by any digital or physical records. We don't really have some well built documentation for those because they are all made.
00:01:07 Interviewee 3
Many past few years and by for more staff and when we would like to do some modification of upgrading. It's very hard to find what to do and how to do and especially the.
00:01:26 Interviewee 3
Tables and the console panel. I'm not sure but but yeah.
00:01:36 Interviewer
Yeah. Yeah, that's fine. Yeah.
00:01:42 Interviewer
Kind of like there's no documentation.
00:01:44 Interviewer
Again, is there yeah.
00:01:46 Interviewee 3
New documentation.
00:01:51 Interviewee 3
Sometimes we lose. We even don't.
00:01:54 Interviewee 3
Know how to access the server from that.
00:01:56
Yeah, yeah.
00:01:58 Interviewee 3
Yeah, but do we even know the user?
00:02:04 Interviewer
Yeah. Well, exactly. Yeah. Unable to access devices.
00:02:11 Interviewee 3
Switches to both sides, so there's.
00:02:19 Interviewee 3
Yeah. OK, fine. Yeah.
00:02:29 Interviewer
Most of them didn't even have a warranty. Right now, I don't think those Cisco switches have anything those those two nine 50s have been out of warranty for maybe a decade. So OK, fine, OK.
00:02:42 Interviewer
UM.
00:02:46
That's good.
00:02:47 Interviewer
So what do you think we?
00:02:48 Interviewer
Could do to improve on it.
00:02:51 Interviewee 3
Well, first.
00:02:54 Interviewee 3
And most important, we need to get the error information. We can do like.
00:03:02 Interviewee 3
Switch ports and the.
00:03:06 Interviewee 3
And their cables, their Connexions and.
00:03:10 Interviewee 3
And and some information about service. What were they doing? What are they? What are they doing on the on the who's the user? The owner of the?
00:03:23 Interviewee 3
And then.
00:03:27 Interviewee 3
Animation switches the traffic because there are some bottlenecks in our switch.
00:03:37 Interviewee 3
It needs to be.
00:03:41 Interviewee 3
Well considered to how to present data and should be.
00:03:50 Interviewee 3
Either way, to get the data in the in the platform or in.
00:03:54 Interviewee 3
The the whatever would be to record the that. Yes, yeah, OK let's say.
00:04:09 Interviewer
I mean like these recordings, I'm literally if I forget what you say, I'm gonna use it so it doesn't go into anywhere.
00:04:13 Interviewer
Yeah. So if you, I wouldn't. Don't don't stress about it entering data into a.
00:04:17 Interviewer
System needs to be like.
00:04:21 Interviewer
Essentially so like I looked earlier for like alternatives and they're all like these massively complicated.
00:04:29 Interviewer
Websites and stuff, they're just this one is really just. It just looks bad.
00:04:34 Interviewer
Another one I found earlier then is just like.
00:04:41 Interviewer
This one here is so over, like complicated sunbird DWIM.
00:04:50 Interviewer
Look at look at the SAT on this now.
00:04:53 Interviewer
Is slow, like really slow then?
00:04:57 Interviewer
So if you want to look at.
00:04:58 Interviewer
Interviewee 3ke visualisation or something.
00:05:02 Interviewee 3
OK.
00:05:10 Interviewee 3
Wow, it's too digital model for like.
00:05:19 Interviewer
Instructions for a data centre that makes sense isn't.
00:05:23 Interviewer
Is but something we've got.
00:05:24 Interviewee 3
We, we, we we don't really need these level.
00:05:27 Interviewer
No, exactly. So right. OK. Just just keep on so.
00:05:35 Interviewer
I don't want to cause anything.
00:05:37 Interviewee 3
The problem is our server is not designed.
00:05:41
At very early.
00:05:42 Interviewee 3
Stage it's going to be room up.
00:05:48 Interviewee 3
A bit bit.
00:05:49 Interviewer
Yeah, it's meant to.
00:05:50 Interviewee 3
Be an yeah. Yeah, we we count a.
00:05:56 Interviewee 3
Move everything. But we need to to get the most important informations.
00:06:02 Interviewer
Yeah. So like the the stuff that might be important for like a A data centre isn't in as as as important to us really, we need to get the fundamentals we need to get the the basic stuff. Yeah, yeah.
00:06:15 Interviewer
OK.
00:06:20 Interviewee 3
The complex system.
00:06:23 Interviewee 3
There is a.
00:06:24 Interviewee 3
Very high thing you need to be trained well to use the system and that costs lots of time and lots of money. Maybe, but it's not suitable for us especially.
00:06:39 Interviewee 3
We we don't have to.
00:06:41 Interviewee 3
Server room humour building and it will be only one in future, yeah.
00:06:48 Interviewer
So to have a massive build software that.
00:06:51 Interviewee 3
Yeah, even though.
00:06:52 Interviewer
The The someone can be complicated. There's only a limit of like how complicated it can be. So like having like a massive softway.
00:07:00 Interviewer
Would be bit, well, unnecessary. Yeah. Yeah, yeah. OK.
00:07:04 Interviewee 3
We overkill and in our.
00:07:14 Interviewer
Any other comments do you think in general though certain stuff? Any ideas you have?
00:07:20 Interviewee 3
Let me think.
00:07:24 Interviewee 3
And when talking about the like.
00:07:31 Interviewee 3
Adding information is very important things to.
00:07:36 Interviewee 3
Build a easy method of human friendly method to to do it, yes.
00:07:45 Interviewee 3
Interviewee 3ke counting the cables and the which port are connected from which device to which speech and it's better to make some.
00:08:05 Interviewee 3
Separate pages, web page or applications on your forms do it because in.
00:08:12 Interviewee 3
We will carry on. We're taking a laptop. It's very hard to working in a narrow corridor in the server room. So for my application, I think it's it's the best way to.
00:08:24 Interviewee 3
Do it. Yeah. OK, yeah.
00:08:27 Interviewer
So working on laptop in narrow spaces.
00:08:29 Interviewer
Is hard. Yeah, definitely.
00:08:39 Interviewer
Yeah. So I'd like to make it on a mobile app would make it easier with many simple forms. For example. Yeah. OK.
00:08:47 Interviewer
Fine. OK. Yeah, great. OK, so I'll explain now what my plans are for my project.
00:08:56 Interviewer
I want to, as you know, we've adopted netbox for all of our kind of data connexion stuff using their API, only making mobile app that.
00:09:08 Interviewer
Allows you to add Connexions, view them, visualise them and stuff like that. So like you said, you can click on a device and see a switch all the Connexions they've got where they are, or cables, they they have that kind of thing, but also power as well. Yeah, so you know, there's some parts of net box, there might be limiting.
00:09:29 Interviewer
So I'm hoping that this can kind of, you know, kind of add on to it. Obviously it's not meant to replace like a full solution of like networks, but it's meant to kind of just.
00:09:38 Interviewee 3
We we do some.
00:09:41 Interviewer
Yeah, exactly. Yeah, yeah. OK, so do you.
00:09:45 Interviewer
Have any kind of you know?
00:09:47 Interviewer
Other than what you've said or any kind of.
00:09:48 Interviewer
Any suggestions?
00:09:49 Interviewer
So you know for for this kind of.
00:09:51 Interviewer
App so you.
00:09:52 Interviewer
Said already, that needs to have a a simple.
00:09:55 Interviewee 3
Simple way to add information. Yeah, you know the home screen is not as big as laptops, so it's hard to really promotion and and.
00:10:10 Interviewee 3
You need to.
00:10:12 Interviewee 3
To think about how to present the data you know, maybe we just leave the most important data when we're using the phone to build the infrastructure or something else. But it's also important, not important, but maybe it's helpful to.
00:10:32 Interviewee 3
Provide some basic tools like ping.
00:10:40 Interviewee 3
Of something because you really.
00:10:43 Interviewee 3
Interviewee 3ke to.
00:10:45 Interviewee 3
The chat the the service status in real time and just some basic basic command would be helpful.
00:10:59 Interviewer
OK.
00:11:01 Interviewer
Probably what quite interesting is if say for example.
00:11:06 Interviewer
I wonder if there's a way to.
00:11:07 Interviewer
Have like an.
00:11:07 Interviewer
Embedded SSH connexion.
00:11:10 Interviewer
You know, you know, like a a console comes up, obviously not a type commands out, but kind of like having. You know you could.
00:11:17 Interviewer
Even if you.
00:11:18 Interviewee 3
If you provide counsel that's that's would be.
00:11:22 Interviewee 3
Brilliant, yeah.
00:11:27 Interviewee 3
But we're we're struggling plugging monitors and moving monitors everywhere from the server to another server and deal with the cables. If you can do.
00:11:36 Interviewee 3
The access it remotely on your phone, it's.
00:11:39
OK.
00:11:41 Interviewee 3
And you don't have a laptop, but you can easily.
00:11:46 Interviewee 3
Access from your phone.
00:11:47 Interviewer
So I wonder whether obviously most of our.
00:11:51 Interviewer
Devices are on different Vlans, so accessing them via states you need to be on say VLAN 22 or 23.
00:11:59 Interviewer
One thing is I'm thinking.
00:11:59 Interviewee 3
And that's a problem.
00:12:01
Do you reckon?
00:12:01 Interviewer
They'd be OK if you could plug a router into say VLAN 22 or something. Well, and then have a device so like only this only like 1 phone could go on there.
00:12:11 Interviewee 3
The the the form is restricted in the server room. That's the.
00:12:17 Interviewee 3
It's safety, but yeah, that's that's a good idea. Think we need to consider about.
00:12:23 Interviewee 3
The safety risk.
00:12:25 Interviewee 3
And because if you provide wireless signal it's not restricted to the room. The people around the room will detect that, yeah.
00:12:36 Interviewee 3
And yeah.
00:12:37 Interviewer
OK. Yeah. We're thinking about. OK, fine.
00:12:42 Interviewee 3
But yeah, it's a good point.
00:12:46 Interviewee 3
Yeah. OK. Or you can use some proxy to like proxy proxy in October?
00:12:53
Oh yeah.
00:12:56 Interviewee 3
We already have got an app from opulence and make it at the middleman and to pass the command.
00:13:06 Interviewee 3
To the active server.
00:13:06 Interviewer
Yeah. OK, that's yeah. That's a good shot. OK. And then maybe then like hard coding some common commands. So like like you?
00:13:14 Interviewer
Said so, if you've got a.
00:13:16 Interviewer
Session open. I don't know. Interviewee 3ke uh.
00:13:21 Interviewee 3
That could be.
00:13:23 Interviewee 3
Really interesting job to investigate but.
00:13:27 Interviewer
Yeah. So we can look at that. Yeah. OK, good. OK.
00:13:30 Interviewee 3
Simulator live session from so yeah, OK yes.
00:13:38
We can.
00:13:40 Interviewee 3
Yeah, if you can look at some existing solutions, then maybe some.
00:13:45 Interviewer
Yeah, OK. I I, I do have one and I'll we'll have a look at that in a second. See if you have any ideas, I would any existing.
00:13:57 Interviewer
OK, right. Well, not look at that quickly actually.
00:14:05 Interviewer
So I've got admin hands is what I use.
00:14:15 Interviewer
There we go. So this is where it's kind of like. So you kind of have obviously the you can type out certain commands and stuff.
00:14:24 Interviewer
Obviously you don't wanna be executing big commands in this to you, so maybe like have like a certain list of commands that might be helpful.
00:14:31 Interviewee 3
OK. Yes, yes.
00:14:32 Interviewer
Yeah. So like so instead of having these buttons here like have like a list of things that could be executed.
00:14:40 Interviewee 3
I'm thinking yeah, please we.
00:14:46 Interviewee 3
Certificate people can access this application. We could provide a list, but yeah, it depends.
00:14:55 Interviewer
Or just this.
00:14:56 Interviewer
That would be OK. Yeah. OK.
00:15:00 Interviewee 3
Because we, we, we we need the.
00:15:02 Interviewee 3
The access to the server.
00:15:04 Interviewer
Yeah. So you know, even though a keyboard isn't necessarily a bad thing, so this kind of thing is.
00:15:10 Interviewer
Quite good. Yeah. Yeah.
00:15:10 Interviewee 3
Ah, if something.
00:15:13 Interviewee 3
Yeah, to run and some tab problems.
00:15:16 Interviewer
OK, so maybe also then so see how this automatically connected to it, maybe there there might be a way I can have a look at.
00:15:28 Interviewer
Kind of accessing like same credentials. Hmm. So say for.
00:15:32 Interviewer
Example you log in with.
00:15:34 Interviewer
Your net box account, whether there's some way we can still finish this?
00:15:37 Interviewee 3
It has less a.
00:15:39 Interviewee 3
Privilege to land the.
00:15:40 Interviewer
Rules. Yeah, of course, you know.
00:15:42 Interviewer
Non non white privilege, they're kind.
00:15:43 Interviewer
Of like a yeah.
00:15:45 Interviewer
OK. Hmm. Well, maybe it just prompts you to enter something just for security wise. Again, it's easier than carrying a laptop. That so. OK, fine. Right. OK, if we move on to the prototypes.
00:15:58 Interviewer
So these are literally just.
00:15:59 Interviewer
5 frames of kind of what I had in mind. Right? OK, so.
00:16:06 Interviewer
So to add, say for example add a connexion.
00:16:12 Interviewer
So I kind of went through.
00:16:14 Interviewer
The the simple kind of.
00:16:16 Interviewer
Following one map box where he has where you choose the rack, choose a device.
00:16:19 Interviewer
And choose the interface.
00:16:21 Interviewer
Yeah. Now this is quite slow.
00:16:24 Interviewer
Because you have to kind of cycle through rack to device, yes.
00:16:29 Interviewer
Uhm, but without? Then. So do you think there's any ways you can improve it right now? So you choose side a new side B and a new scanner cable.
00:16:38 Interviewer
You want to add then the cable type, so then that would be like CAT5CAT6 cat seven that kind of.
00:16:43 Interviewer
Thing or power. So do you have any kind of?
00:16:46 Interviewer
Comments on that one and.
00:16:50 Interviewee 3
If you can.
00:16:51 Interviewee 3
Find an easy way to locate the device.
00:16:56 Interviewee 3
Rather than to like the rap, the site, the room and the device from the Scroll down list. Or we can add labels on server.
00:17:09 Interviewee 3
And scan with the same way as cables.
00:17:14 Interviewee 3
And it could be.
00:17:15 Interviewee 3
Very fast, but it walks to the.
00:17:18 Interviewer
That's fine. I was planning to do.
00:17:20 Interviewer
That anyway, but it sounds better come from someone else. So then I can quote you saying.
00:17:25 Interviewer
That's a good idea.
00:17:26 Interviewer
Yeah. So I was planning to do.
00:17:28 Interviewer
That anyway. So my plan is eventually to have literally you have a label on the device scan that, yeah, scan a cable, scan the other device, and then a connected that's essentially white plan.
00:17:39 Interviewer
But what we currently have is that way. But what I've done in the meantime is I've kind of gone and I think you suggested it when I was in.
00:17:48 Interviewer
When I showed you originally.
00:17:51 Interviewer
Is that you can search for a device now if.
00:17:53 Interviewer
I do it in dark mode.
00:17:54 Interviewer
So you can kind of search for one inside.
00:17:56 Interviewer
Now so like.
00:17:57 Interviewer
I don't know Deadpool.
00:17:59 Interviewer
Hmm, so Deadpool, now you can kind of select it or I don't know, CFF one or four because I know they've got. So then there's that, Wayne said. So it's a bit quicker. Mm-hmm, you know.
00:18:09 Interviewee 3
Yeah, yeah. The slide function is pretty good.
00:18:13 Interviewer
Yes, it's quite smooth, isn't it? But so you can kind of and then open the barcode scanner scan and it's done.
00:18:14 Interviewee 3
Yeah, yeah.
00:18:18 Interviewer
But what I'd like to do is be able to literally have scan device a scan device.
00:18:22 Interviewer
B. Choose the interface.
00:18:24 Interviewee 3
And again, the cable. Yeah. And to the interface.
00:18:24 Interviewer
You know.
00:18:28 Interviewer
OK, fine. OK, that's good.
00:18:30 Interviewer
OK, so Labourd on devices to scan, so you only need.
00:18:44 Interviewer
OK. OK. So view connexion, now the very simple one, you can't keep, that's the entire idea really, isn't it?
00:18:53 Interviewer
But I've also then done a search by device as well, just in case. If for example the cable is that you can't find the bar code.
00:19:00 Interviewer
Interviewee 3ke that? Yeah, so.
00:19:02 Interviewer
Kind of the same thing. Here is where you could instead of choosing the rack and choosing the device, you could scan the device label instead and then choose the interface. That's right. Yeah. OK, so.
00:19:22 Interviewee 3
You cannot.
00:19:26 Interviewee 3
So Zoom Network has some visualisation like we all.
00:19:34 Interviewee 3
If you if you see a switch and a release.
00:19:39 Interviewee 3
Every device connected to it which device is on the which port? Yeah. OK.
00:19:45 Interviewer
So it doesn't have that kind of like it doesn't like show you the switch. If you think of you thinking like like a patch panel.
00:19:57 Interviewer
Visualisation so.
00:20:01 Interviewer
So do you mean something like like like that?
00:20:04
That's the that, that's.
00:20:05 Interviewee 3
The perfect one, but I'm not. I'm not pursuing it.
00:20:09 Interviewee 3
Yeah, like even the task form is, is. It's. Yeah, it's fine.
00:20:14 Interviewer
So if we look at what?
00:20:15 Interviewer
I did the other day, so we go to.
00:20:22 Interviewer
So you know.
00:20:22 Interviewer
When I was showing you the demo today, so you can see the Connexions like this.
00:20:28 Interviewer
Interviewee 3ke that, yeah.
00:20:30 Interviewer
Interviewee 3ke is that.
00:20:30 Interviewer
Is that where you?
00:20:31 Interviewer
Kind of mean kind of something simple like that.
00:20:34 Interviewer
So you can see this so device device type location and then.
00:20:39 Interviewee 3
One to one, one to one, yeah.
00:20:42 Interviewer
But I think there's.
00:20:43 Interviewer
Also a way then you can have it so it kind of if there's a a connexion between multiple devices you can kind of follow it through. Yeah, yeah.
00:20:49 Interviewee 3
And create rules.
00:20:51 Interviewee 3
Create the rules.
00:20:54 Interviewer
And net proxy API allows you to kind of get all these devices as well. So Netbox can will do the trace for you.
00:21:02 Interviewer
So what I can do is I can kind of replicate this kind of design here. Yeah. And then kind of get down the phones, you can almost scroll through the Connexions so you know where it starts when it finishes.
00:21:12 Interviewer
Yeah. OK. So that so for this kind of rough one here, I've kind of just got a this is the cable, this is the device.
00:21:22 Interviewer
Where it is that kind of thing there. So that would be the device, that's the where it is in the rack, that's the rack and that's the interface.
00:21:31 Interviewer
Now that's kind of, you know, do you have? So do you think then that this?
00:21:35 Interviewer
Kind of thing would be better.
00:21:38 Interviewee 3
One thing came if you if your prototype it's more suitable for phone screen.
00:21:40
That if that.
00:21:49 Interviewee 3
Case this kind of design will require.
00:21:55 Interviewee 3
It has more information on it than density of information. Maybe it's it's it's higher so then.
00:22:06 Interviewee 3
I'm not sure, OK, but if you can trace it.
00:22:10 Interviewee 3
Can can screw down or screw up and you can trace the route. That's better is the screw.
00:22:17 Interviewer
Idea about this kind of thing?
00:22:19 Interviewee 3
Yeah, that's great.
00:22:21 Interviewer
So then more you'd be able to. Then you could say for.
00:22:23 Interviewer
Example, scroll through it.
00:22:25 Interviewer
So like like here.
00:22:26 Interviewer
You can say that's the device.
00:22:28 Interviewer
And that's the type. That's where it is. Mac address IP address? Or is that? Do you think that's too much information on there?
00:22:36 Interviewee 3
Not dresses is good, is good.
00:22:40 Interviewer
And then these are then this is the interface that's the type of interface.
00:22:44 Interviewer
So like 1 Gigabit.
00:22:46 Interviewer
Then that's the cable, and that's the cable to then.
00:22:48 Interviewer
And then you know, so then like you said then so say for example, then if there was like a multiple devices, then you'd be able to then?
00:22:56 Interviewer
Kind of Scroll down and then see then.
00:22:59 Interviewee 3
You'll see in the metre.
00:23:00 Interviewer
Yeah. What's the middle? That kind of thing? So you can Scroll down and like, see then where it goes to. Yeah, that.
00:23:05 Interviewee 3
Right.
00:23:06 Interviewer
Kind of thing, OK.
00:23:08 Interviewer
Yeah. OK, that sounds good.
00:23:11 Interviewee 3
And because you assume you've got every network information, we will generate some topology of the network devices.
00:23:23 Interviewer
Yeah. So viewing the topology.
00:23:26 Interviewer
Would be quite good as well with it OK.
00:23:29 Interviewee 3
So if you would like to.
00:23:30 Interviewer
OK.
00:23:32 Interviewee 3
Have a a better view on your laptop and it's. You can see the entire topology of the room. That's.
00:23:42 Interviewer
Really helpful. Yeah.
00:23:44 Interviewee 3
And there are some concerns.
00:23:47 Interviewer
Yeah. OK. I'll look into that. OK. So then.
00:23:53 Interviewer
Also, then there's some things that are just very simple ones. So like kind of like add an interface.
00:23:58 Interviewer
Would be you.
00:23:59 Interviewer
I'd again, I'd replace that with scanner device thing you know.
00:24:04 Interviewer
So you just scan a device and you had the interface, but also then that's only having one interface. So do you think there needs to be?
00:24:11 Interviewer
An option to add multiple as well.
00:24:13 Interviewer
At the same time.
00:24:21 Interviewee 3
It depends on.
00:24:22 Interviewee 3
The the type of of the device. If you have multiple device like multiple interface like Switch, you can add it.
00:24:25 Interviewer
OK.
00:24:36 Interviewee 3
More than one.
00:24:38 Interviewee 3
Or at at the same time. But if that's a normal server, it won't have.
00:24:45 Interviewee 3
Yeah, 10s or 20 interface. You just have maybe 4:00. That's fine for adding one by.
00:24:52 Interviewer
One. So maybe having an option where you can create one and then make bulk.
00:24:56 Interviewee 3
Yeah, right.
00:24:58 Interviewer
Yeah. So like, like, you know, like in that box how you can like we can specify like a prefix.
00:25:03 Interviewer
So it's like.
00:25:05 Interviewer
GE underscore one through to 40.
00:25:07 Interviewee 3
8 and then yeah.
00:25:09 Interviewer
Yeah, but then also then be able to make one as well. So like, you know, literally like.
00:25:15 Interviewer
So like if it's like a management port for example, that kind of.
00:25:19 Interviewer
Thing as well. Yeah. OK.
00:25:24 Interviewee 3
So you can add one more one and you can add a bunch.
00:25:27 Interviewer
Of them? Yeah, that's that's fine. Yeah. OK, cool. OK.
00:25:35 Interviewer
And then if we look at so sure devices, then again I think you'll be very like I said earlier, be simplified by just scanning the device label then what kind of information would you want to see on it?
00:25:50 Interviewee 3
OK.
00:25:54 Interviewee 3
You know, especially they, they, they.
00:25:59 Interviewee 3
The interface Connexions OK and I'm assuming it's.
00:26:10 Interviewer
So it's limited to.
00:26:11 Interviewee 3
IP sorry faces. So the the network things is is a big thing. Yeah, big thing we we. But we need to see something else.
00:26:23 Interviewee 3
Interviewee 3ke about the.
00:26:26 Interviewee 3
Some yes.
00:26:28 Interviewee 3
Because some some, some server has very special hardware settings, not not settings like.
00:26:37 Interviewer
Specs like the CBL yeah.
00:26:39 Interviewee 3
See we all.
00:26:40 Interviewee 3
Have some.
00:26:42 Interviewee 3
GPU service. Yeah, we can make the yeah. OK.
00:26:51 Interviewer
So if I look at, say, Deadpool.
00:26:56 Interviewer
So Michael has put in kind of all this information here.
00:27:00 Interviewer
So like it's got.
00:27:01 Interviewer
The CPU information network interfaces all that kind of thing's.
00:27:06 Interviewer
Already done now.
00:27:07 Interviewer
See, that's what he's done for those.
00:27:10 Interviewer
I was probably thinking of doing a bit more of a a standard one for each one, so like CPU, RAM, you know?
00:27:18 Interviewer
That kind of thing.
00:27:20 Interviewee 3
Hmm, what's this? What's this Jason kind of thing?
00:27:24 Interviewer
So he's made himself OK? Yeah.
00:27:26 Interviewee 3
It's the format that he made.
00:27:28 Interviewer
Yeah, yeah, all these kind of exported it from somewhere, I don't know, but.
00:27:33 Interviewee 3
I'm I'm suspect it's exported from somewhere.
00:27:36 Interviewer
Yeah, because it kind of looks like it.
00:27:37 Interviewer
Is. Yeah, it might be.
00:27:39 Interviewer
From the devices themselves? Maybe that's why I'm asking.
00:27:43 Interviewer
OK.
00:27:48 Interviewer
OK, OK. OK, what else do we have here? Lastly, all the kind of rest of these things are very much.
00:27:59 Interviewer
Kind of deleting the information, deleting things. So as far as seeing the device information, I've kind of gone for this kind of like drop down thing so you can kind of so it's not too much at.
00:28:10 Interviewer
Once you can kind of you kind of group it down. So like when you click this button then it expands to yeah.
00:28:19 Interviewee 3
But thinking we have.
00:28:21 Interviewee 3
View viewing we have adding we have deleting and.
00:28:27 Interviewee 3
But there's another thing going to be happen that's.
00:28:32 Interviewee 3
Upgrading or changing?
00:28:34 Interviewer
Changing stuff, yeah.
00:28:35 Interviewee 3
Yes, modifying.
00:28:37 Interviewer
From flight device.
00:28:38 Interviewee 3
51 to the new one status. Maybe not one.
00:28:45 Interviewer
OK. Yeah.
00:28:48 Interviewer
So what? What kind of things, obviously.
00:28:51 Interviewer
So we can obviously update the connexion. That's the last thing that's that's yeah. So if you're updating devices, what do you think could be I think that it can be very easily done to kind of do too much. So say for example updating like I don't know.
00:28:54 Interviewee 3
Interviewee 3ke so big.
00:29:09 Interviewer
Interviewee 3ke the hardware for example that.
00:29:10 Interviewer
Can be done our laptop coming?
00:29:12 Interviewer
In the office.
00:29:18 Interviewee 3
Can you please expand explain again about the?
00:29:23 Interviewer
Is that so?
00:29:27 Interviewer
You know, so if you want to, like, update things about your device, it can be in get like too, too much to, you know, if you're in the server room, there's no need to.
00:29:36 Interviewer
Do it in the server room to.
00:29:42 Interviewee 3
My this discussion in my mind is like we would like to change the connexion you're in the server room and you found the the server connexion is not correct or need to be modified.
00:29:56 Interviewee 3
You unplug it.
00:29:58 Interviewee 3
Unplug one cable from the from the switch. Yeah, and you.
00:30:04 Interviewee 3
Plugged into another port. Yeah, and that's.
00:30:06 Interviewer
It well, yeah. So after that that.
00:30:10 Interviewer
Then you'd scan. You'd scan one side, you scan the cable, and you scan the switch.
00:30:13 Interviewee 3
Yeah, you can. You can like kind of reuse the adding page I think yeah. And for it to update the information.
00:30:21 Interviewer
Yeah, yeah.
00:30:21 Interviewer
So like I've got here update connexion.
00:30:24 Interviewee 3
OK.
00:30:25 Interviewer
Yeah. So you then you update, so you choose then so say for example you're updating the inside, you only change one.
00:30:33 Interviewer
You know, so you just kind of like side. So what the idea is, is that I'll fill the information here with what it currently is.
00:30:41 Interviewer
Right. So say for example, it would be it would show like. I don't know it would show Deadpool and then would be like I don't know, uh E one or zero one for example so.
00:30:53 Interviewer
To get rid of that. So that's why it would show then if you want to update Deadpool side then you could then just click on Deadpool and then you just change.
00:31:01 Interviewer
It to that.
00:31:02 Interviewee 3
It was based on the cable.
00:31:05 Interviewer
Yeah. So you scan the cable.
00:31:07 Interviewee 3
You scan the.
00:31:08 Interviewee 3
Cable first and tell the tell which port.
00:31:10 Interviewer
Then it pops up with woman, yeah.
00:31:13 Interviewee 3
Which Newport that they have, OK.
00:31:15 Interviewer
Yeah. Yeah. OK.
00:31:18 Interviewer
Also like when when I get a prototype working, I can then kind of show you what what I mean properly OK.
00:31:27 Interviewer
Any other kind?
00:31:28 Interviewer
Of thing. So I kind of got like a little suggestion here where it's like you've got some links to some things. So like netbox online.
00:31:36 Interviewer
So it kind of takes you just opens on the web browser. So say for some of this thing missing. You know that kind of thing slide.
00:31:44 Interviewer
Just just some quick.
00:31:45 Interviewer
Interviewee 3nks. Do you think they needed?
00:31:48 Interviewee 3
If you wanted to make a, make a big entry, that's great, yes.
00:31:54 Interviewee 3
And but.
00:31:57 Interviewee 3
Third time.
00:31:59 Interviewee 3
The the server the server need start management.
00:32:03 Interviewer
No, not really. OK. True. Yeah. OK, don't blink.
00:32:12 Interviewer
Fine. OK.
00:32:17 Interviewer
Anything else you any ideas? Anything you?
00:32:20 Interviewer
Not seeing.
00:32:23 Interviewer
Yeah. Everything by. Yeah. Yeah, fine. Yeah. Yeah. OK. What if I just then show you quickly then.
00:32:27 Interviewee 3
Thanks fine.
00:32:34 Interviewer
UM.
00:32:37 Interviewer
So if I show you now these little demos things here very quick, just like cover like some.
00:32:43 Interviewer
What you think about them?
00:32:47 Interviewer
So you don't that's that's one. So this one here is called DC track by Sunbird.
00:32:56 Interviewer
Interviewee 3ke you said earlier, it's kind of so these are the kind of how you view the assets and stuff. They just kind of list them and they kind of philtre it by like cabinet for example.
00:33:08 Interviewee 3
Well, I think that this is a good point because we don't have such.
00:33:16 Interviewee 3
And in the spreadsheet.
00:33:18 Interviewee 3
To Philtre every field. Yeah. And networks. And sometimes we we have to choose. Interviewee 3ke you can you can view everything in in one rack that you can view.
00:33:37 Interviewee 3
With our device across different rocks. Yeah. OK, there's a there's an entirely, but you can philtre them. Yeah. Fill them one by.
00:33:48 Interviewee 3
One yes, just locate.
00:33:49 Interviewer
It's OK.
00:33:51 Interviewee 3
In the same page they they they often do.
00:33:56 Interviewee 3
Get you to a new page and.
00:33:58 Interviewer
It's a bit inefficient, isn't it? Kind of.
00:34:02 Interviewer
Do you wanna look around and see what you think about this? Just as comparing it to to net box maybe?
00:34:12 Interviewee 3
Now when?
00:34:14 Interviewer
I think you're gonna.
00:34:18 Interviewee 3
Yes, because we want to find some device and.
00:34:27 Interviewee 3
I can do search here but.
00:34:33 Interviewee 3
Interviewee 3ke that pool.
00:34:41 Interviewee 3
If I go here.
00:34:44 Interviewee 3
There's only one philtre you can you can. You can. You can search you can't. You can't philtre to Philtre specific.
00:34:54 Interviewer
Rise, I see, yeah.
00:34:57 Interviewee 3
I think this is very kind of helpful.
00:35:01 Interviewer
OK.
00:35:06 Interviewee 3
There are two allow me to tap, yeah.
00:35:09 Interviewer
Yeah as well. OK, so look.
00:35:17 Interviewer
Do I just?
00:35:17 Interviewee 3
I don't.
00:35:18 Interviewee 3
I don't like this.
00:35:19 Interviewer
No, because it's like why you?
00:35:20 Interviewer
Why is it on your tab kind of thing?
00:35:22 Interviewer
I mean it cause you can kind of you.
00:35:24 Interviewer
Can click on these where it's like it.
00:35:25 Interviewer
Sorts them, yeah.
00:35:28 Interviewer
OK, I suppose this kind of this kind of searching.
00:35:31 Interviewer
Would be.
00:35:33 Interviewer
Wouldn't you wouldn't need it if you're in.
00:35:37 Interviewer
If you can scan it, will you?
00:35:39 Interviewee 3
Yeah. So.
00:35:41 Interviewee 3
If I can scan the selfie, it's fine, yeah.
00:35:44 Interviewer
So maybe kind of.
00:35:46 Interviewee 3
We were sitting in the office.
00:35:50 Interviewee 3
Yeah, best way.
00:36:01 Interviewer
OK.
00:36:05 Interviewer
And is there anything you kind of you don't?
00:36:07 Interviewer
Interviewee 3ke about this.
00:36:11 Interviewer
I mean, like any any kind of features.
00:36:14 Interviewer
And like, do you?
00:36:14 Interviewer
Think there's thing we need that.
00:36:18 Interviewee 3
Oh, it's driven by the data. Yeah, basically. Yeah. It's all like things like it's.
00:36:36 Interviewee 3
If I would like to add something.
00:36:40 Interviewee 3
How do I do it?
00:36:45 Interviewee 3
And the device.
00:36:47 Interviewee 3
A new item.
00:36:53 Interviewee 3
All right.
00:36:56 Interviewer
Wow, it's really slow.
00:37:03 Interviewee 3
Click turn on times and.
00:37:16 Interviewer
You need to kind of imagine you value you SO2950 slow, isn't it?
00:37:28 Interviewer
There we go.
00:37:31 Interviewee 3
It has a like a preset database.
00:37:35 Interviewer
I think so.
00:37:41 Interviewer
Wow, this is a lot of information.
00:37:47 Interviewer
Do you think this is a?
00:37:48 Interviewer
Bit kind of overwhelming.
00:37:49 Interviewer
Compared to that box, yeah.
00:37:52 Interviewer
Think that box is a bit.
00:37:53 Interviewer
Better do you think?
00:37:54 Interviewee 3
That box is more lightweight I think.
00:37:57 Interviewee 3
There's too much information.
00:38:02 Interviewer
Well, yeah, all at once as well.
00:38:06 Interviewer
OK.
00:38:20 Interviewer
OK, so if I you know if if it's if it's so you can kind of take from that?
00:38:24 Interviewer
As in in the mobile.
00:38:27 Interviewer
App. Obviously that's what we've.
00:38:28 Interviewer
That's what I'm gonna be doing. I'm not gonna replacing that box entirely, obviously.
00:38:34 Interviewer
Do you think that this kind of filtering so they're filtering on that box like say for example you know like when you're searching for an asset to the filtering like filtering so.
00:38:46 Interviewee 3
You want to you want. I don't want to do this. I'm. I'm on my phone. Maybe on the laptop.
00:38:53 Interviewer
Yeah. OK, fine. Yeah. You don't want that kind of all this kind of thing on your phone? No.
00:38:59 Interviewer
Yeah, but maybe being able to search so maybe you could like say for example select something to search through.
00:39:07 Interviewer
So you know.
00:39:08 Interviewer
Interviewee 3ke how on on that box you can.
00:39:13 Interviewer
You know, I hear you. If you say like, like Jean maybe.
00:39:17 Interviewer
It kind of comes up with both like.
00:39:20 Interviewer
You can. So maybe if you feel if.
00:39:23 Interviewer
I have like a drop down box.
00:39:24 Interviewer
So search by something. Mm-hmm. And it comes up. Then it philtres it so it gets all the devices. So for example, they're owned by. Don't know. Going to across. So if you search by.
00:39:40 Interviewer
And then all the Jerry Tycroes ones come up. Yeah, OK.
00:39:42 Interviewee 3
It's useful, yeah.
00:39:44 Interviewee 3
This can be this can be on the.
00:39:48 Interviewer
Yeah. Yeah. OK. I can look into that, right.
00:39:54 Interviewer
OK, Netbox then so I go to demote on that box just to kind of.
00:40:06 Interviewer
I mean you've.
00:40:06 Interviewer
Got quite a lot of experience in that books.
00:40:08 Interviewer
Now and you kind.
00:40:08 Interviewer
Of know how it works and stuff.
00:40:13 Interviewer
Yeah. OK.
00:40:16 Interviewer
I mean, you know now how to kind of, I mean you can you know how to add.
00:40:19 Interviewer
The voice and stuff.
00:40:20 Interviewee 3
Interviewee 3ke that. I know, yes, yeah.
00:40:25 Interviewee 3
Devices so the networks doesn't have like programmes.
00:40:31 Interviewee 3
Information for the device make and model, so we need to add them manually at first. Yeah, that could be a little bit.
00:40:43 Interviewee 3
Tedious, yeah.
00:40:45 Interviewee 3
The and if if we found we did something wrong and we already.
00:40:52 Interviewee 3
Create some device from that template. It's a little bit.
00:40:58 Interviewee 3
Painful. Yeah. OK, what?
00:41:02 Interviewer
About if we think about it in the use of.
00:41:05 Interviewer
If you would.
00:41:06 Interviewer
Use on the phone like in.
00:41:08 Interviewer
In the server.
00:41:09 Interviewee 3
Room in the server room? Yeah, I.
00:41:14 Interviewee 3
Uh in the server room we trying to create templates.
00:41:21 Interviewee 3
Yeah, we we did that and.
00:41:32 Interviewee 3
Return plate but.
00:41:36 Interviewee 3
Well, it's hard to do it on mobile phone. We need to search the information from Google.
00:41:45 Interviewer
Yeah. So it's yeah, it's not like.
00:41:48 Interviewer
So so you can read through.
00:41:49 Interviewer
In situ use it and I think maybe.
00:41:51 Interviewer
If we look at kind of this.
00:41:52 Interviewer
In mobile as well.
00:41:55 Interviewee 3
Get the data.
00:41:58 Interviewee 3
Oh yeah, that is yes. Or we can just import it.
00:42:06 Interviewer
Before we can import it. Yeah, and.
00:42:08 Interviewee 3
And select what data we want and.
00:42:14 Interviewer
What do you think? So if?
00:42:14 Interviewer
We look at say.
00:42:21 Interviewer
This looks pretty awful, doesn't it?
00:42:23 Interviewer
So this isn't this isn't?
00:42:24 Interviewer
Very intuitive, is it to look at no kind of scrolling through this. This information is just not needed. Yeah, no, it's not. Yeah. OK. Yeah.
00:42:33 Interviewee 3
The human readable.
00:42:48 Interviewee 3
Existing tools are not designed for mobile phone.
00:42:53 Interviewee 3
So we should.
00:42:56 Interviewee 3
Should make out on you.
00:42:58 Interviewer
Yeah. So that's.
00:42:59 Interviewer
Where? That's where the kind of thing is.
00:43:00 Interviewer
Is that I I've looked.
00:43:02 Interviewer
Interviewee 3ke quite hard for kind of things for your phone and it just doesn't exist. And I can.
00:43:07 Interviewer
Understand why for like if.
00:43:09 Interviewer
I work at Google.
00:43:11 Interviewer
I don't think they, you know, they they're not gonna need and maybe they don't need a.
00:43:16 Interviewer
Mobile phone you.
00:43:17 Interviewer
Know they got like these big trolleys.
00:43:18 Interviewer
They can walk around with them.
00:43:20 Interviewer
But in a first scenario like I was or like well any other small company that has their own servers.
00:43:27
You don't really.
00:43:28 Interviewer
You don't want like.
00:43:29 Interviewer
This all of this kind of all of these features do you?
00:43:32 Interviewer
You don't want like you.
00:43:34 Interviewer
Know all of this kind of visualisation stuff, maybe.
00:43:38 Interviewee 3
Not very.
00:43:44 Interviewee 3
The information to be correct.
00:43:47 Interviewer
Yeah. OK. So quickly we'll.
00:43:50 Interviewer
Just we'll just do this last one quickly.
00:43:53 Interviewer
So this is patch manager, so if we go into mobile again, patch. Yeah. So it's like another free what free one?
00:44:01 Interviewer
So if we go into.
00:44:06 Interviewee 3
Is it focusing on switch you?
00:44:09
It's more so like.
00:44:10 Interviewer
Yeah, it's more so for networking more than anything.
00:44:17 Interviewer
So let's go. Let's go into.
00:44:19 Interviewer
Test location.
00:44:21 Interviewer
OK, so this kind of thing.
00:44:25 Interviewer
So then if you don't click.
00:44:26 Interviewee 3
On the the touch experience will be will be awful, but the viewing looks looks not so bad.
00:44:37
OK.
00:44:38 Interviewer
So there's some things about it. So like the kind of this kind of view of the cabinet isn't very good on mobile.
00:44:45 Interviewer
Whereas if it was like a.
00:44:49 Interviewer
It was essentially Christ I.
00:44:50 Interviewee 3
Think think so.
00:44:52 Interviewer
Yeah, it crashed. OK.
00:44:56 Interviewee 3
So so look.
00:44:56 Interviewer
Is any devices.
00:45:01 Interviewer
Let's go to a switch here.
00:45:11 Interviewer
Does that not do anything?
00:45:13 Interviewee 3
Oh, it's crashed game.
00:45:15 Interviewer
I don't, I don't think so because I.
00:45:17 Interviewer
Can still scroll.
00:45:18 Interviewee 3
If you can go back to the laptop view.
00:45:28 Interviewee 3
Ring one.
00:45:30 Interviewer
I don't think. I don't think they do.
00:45:32 Interviewee 3
Anything blue one, but they but the button the buttons need to be.
00:45:39 Interviewer
If I go to.
00:45:41 Interviewee 3
OK.
00:45:44 Interviewer
This templins cabinet.
00:45:48 Interviewer
They do.
00:45:51 Interviewer
OK.
00:45:52 Interviewee 3
OK.
00:45:53
Ah, there we go.
00:45:54 Interviewer
So there's all the information there look.
00:45:57 Interviewee 3
Once you look at it and you won't see.
00:46:01 Interviewer
The sale goes away.
00:46:06 Interviewer
So the UI looks better.
00:46:29
OK.
00:46:33 Interviewer
I think is anything else you.
00:46:35 Interviewer
Kind of, you know.
00:46:37 Interviewer
Anything else you want to say at all?
00:46:40 Interviewee 3
Yeah, I think that's OK, yeah.
