00:00:01 Interviewer
There we go. Right. So Interviewee 2 the 6th of December.
00:00:08 Interviewer
Right.
00:00:10 Interviewer
So the first question is, what are your opinions on the current state?
00:00:14 Interviewer
Of the server room.
00:00:18 Interviewee 2
Massive improvements and.
00:00:24 Interviewee 2 
I mean the future for it is sounds great.
00:00:31 Interviewee 2 
I mean, just just the lighting basically and make them massive amount of difference so.
00:00:35 Interviewer
It's huge.
00:00:39 Interviewee 2 
Not from safety.
00:00:42 Interviewee 2 
Helping with that, you know, just being able to see or you can actually your work, you know seeing what you can do is is just great.
00:00:54 Interviewee 2 
And of course, the Power Distribution as well.
00:01:02 Interviewee 2 
Sort it out properly without.
00:01:06 Interviewee 2 
Risks of tripping?
00:01:08 Interviewee 2 
CD's and things like that. I mean that.
00:01:11 Interviewer
So why it's all kind of.
00:01:13 Interviewer
Coming coming together. Coming. Yeah, so I think.
00:01:20 Interviewer
You know, it's been, I can't imagine what it was like, just to kind of just having just you needing to do all of it and then you've come then to have this team of like well at the peak of of of you need temps it was like.
00:01:32 Interviewer
Six or something.
00:01:34 Interviewer
So you just it was, you know, it was you doing the pandemic and stuff after after Nick left.
00:01:38 Interviewer
Not sure he did, but then he killed me around for a bit as well. But then he kind of then went then from just you to then having.
00:01:45 Interviewer
A team most.
00:01:46 Interviewer
Yeah. So you know a lot of things have been able to be done because I think I think the biggest problem is.
00:01:53 Interviewer
Every day you want to come in, you have to keep the ball rolling.
00:01:55 Interviewee 2 
And I think then, well, I mean, it was massive during the pandemic when all the stuff.
00:02:02 Interviewee 2 
Was happening and then.
00:02:04 Interviewee 2 
Told that.
00:02:06
To move C.
00:02:07 Interviewee 2 
36 downstairs as well and yeah it.
00:02:10 Interviewee 2 
Just felt like.
00:02:11 Interviewee 2 
A massive well, it is a massive job, yeah.
00:02:15 Interviewee 2 
I mean, as you know, it's not just 15 machines often taken down.
00:02:21 Interviewee 2 
This is what?
00:02:23 Interviewer
This had to.
00:02:24 Interviewee 2 
Be like how it was thought about.
00:02:28 Interviewer
Yeah, but.
00:02:31 Interviewee 2 
But yeah.
00:02:34 Interviewer
Yeah, OK. I mean.
00:02:37 Interviewer
Yeah, it was just. It was.
00:02:38 Interviewer
Just it was a massive task of for even a team to yeah, let alone you know.
00:02:44 Interviewee 2 
I mean obviously that.
00:02:47 Interviewee 2 
If C36 had been.
00:02:50 Interviewee 2 
Properly mapped and everything I mean it's just because of lack of people to.
00:02:54 Interviewee 2 
Do it or.
00:02:55 Interviewee 2 
Yeah, yeah.
00:02:56 Interviewee 2 
But if that.
00:02:57
Was all it?
00:02:58 Interviewee 2 
Was documented.
00:03:01 Interviewee 2 
And everything and all the plans were there.
00:03:03 Interviewee 2 
Beforehand. Obviously it would be a lot easier.
00:03:08 Interviewee 2 
But the fact that we're doing that now, so we know just you know where network cables are going, what which which is they're going to which are links are going to.
00:03:16
OK.
00:03:18 Interviewee 2 
You know, and the server rooms and you know and and the.
00:03:23 Interviewee 2 
Wiring centres, you know? Yeah. I mean, yeah, all.
00:03:26 Interviewee 2 
Kind of thing just to know that.
00:03:30 Interviewee 2 
You need to know that anyway. Have it all there and you know.
00:03:38 Interviewer
A massive help. Yeah. You know, I was saying kind of earlier is that, you know this.
00:03:44 Interviewer
I think with the way this has been is cause it's always been. It's been developed incrementally, isn't it young people. So yeah, William started it all off and making its scripts and then.
00:03:53 Interviewer
You know.
00:03:54 Interviewer
And then all you know, all the work you've done and there is buying and and configuring stuff and keeping it going.
00:04:00 Interviewer
And then Michael's come in and dance, come in. And and he's gone now. And that kind of thing. It's that there needs to be like a.
00:04:06 Interviewer
You know, historical.
00:04:08 Interviewer
You know well a change of things as well. But like you said, knowing these things is.
00:04:12 Interviewer
Just a good thing. Yeah. OK.
00:04:17 Interviewer
Do you think you know what? What? What would? What would you say could be improved generally in in in any aspect?
00:04:24 Interviewer
Documenting is in the layout of the cables. Anything like.
00:04:27 Interviewee 2 
That I mean the documenting and.
00:04:30 Interviewee 2 
I was thinking about, you know, with netbox like.
00:04:37 Interviewee 2 
Is it possible just to have like a?
00:04:41 Interviewee 2 
A focus.
00:04:44 Interviewee 2 
You know, so so you've got the plan of the racks and you hover over a PC and you over a server and you can.
00:04:55 Interviewee 2 
Have an option to.
00:04:58 Interviewee 2 
Maybe see the network Connexions from that, or the power Connexions.
00:05:05 Interviewer
So like from from like the?
00:05:07 Interviewer
The elevation, is it? Yeah.
00:05:08 Interviewee 2 
But without.
00:05:11 Interviewee 2 
The other.
00:05:13 Interviewee 2 
Server information that so you can focus on just one server.
00:05:17 Interviewer
OK.
00:05:19 Interviewer
Yeah. So like.
00:05:21 Interviewee 2 
So you hadn't we?
00:05:22 Interviewee 2 
Wouldn't have too much information all at.
00:05:24 Interviewee 2 
Once you could just.
00:05:24 Interviewer
Yeah. Plus, yeah.
00:05:25 Interviewee 2 
See the Connexions for that server to which switch.
00:05:28 Interviewee 2 
And and that.
00:05:30 Interviewer
OK. Yeah, that sounds good. So.
00:05:35 Interviewer
So view of view of devices.
00:05:39 Interviewer
It doesn't kind of overwhelm you with it because you can. You can get so much information. Yeah. You know this like, looking at the the the V Centre APIs like this, thousands of different things. You just don't need to.
00:05:51 Interviewer
Know but yeah.
00:05:55 Interviewer
Possibly our focus view, so a view of devices that just just.
00:05:57 Interviewer
Doesn't overwhelm you, yeah.
00:05:59 Interviewer
So networking, it's a key information really.
00:06:03 Interviewer
Yeah, OK. Yeah.
00:06:05 Interviewer
I think I think that's probably, I mean whether you be doing that box specifically or whether it be done on here would be a different thing, yeah.
00:06:15 Interviewee 2 
I mean, yeah, obviously it's that information would be incredibly usable.
00:06:22 Interviewee 2 
You know in which distribution power board it's going to, yeah.
00:06:36
And then.
00:06:39 Interviewer
Anything else you can think of?
00:06:49 Interviewer
That was what I was thinking. Yeah. Yeah. Just earlier today.
00:06:59 Interviewer
I think one thing I noticed here that I've been that box to the new version, they've kind of extended on their journaling features where you can add you can add like a kind of history, different things and stuff to it. So say for example you know like you know the other day when.
00:07:16 Interviewer
It was a cool one down.
00:07:20 Interviewer
The DHCP issues. Ohh yeah, rusty. Yeah, yeah, rusty and stuff since you know you can add, you can go on to Rusty and you can add like a.
00:07:27 Interviewer
History of, you know, a failure.
00:07:30 Interviewee 2 
Right and wrong, yeah.
00:07:31 Interviewer
You know, and so then in the future then when when?
00:07:34 Interviewer
Something similar happens again. We've got kind of a.
00:07:37 Interviewer
You know.
00:07:39 Interviewer
Yeah. And then having one place.
00:07:40 Interviewer
Kind of thing.
00:07:41 Interviewee 2 
Well, that's it. I mean just.
00:07:45 Interviewee 2 
A description for each server.
00:07:47 Interviewer
Yeah. What is it like what they do? Yeah.
00:07:50 Interviewee 2 
What it's doing?
00:07:52 Interviewer
Yeah, yeah.
00:07:56 Interviewer
OK.
00:07:57 Interviewee 2 
I mean, it's quite a basic thing, but you.
00:07:59 Interviewer
Know well, yeah, I mean just just having it down. Yeah. You know, if it's if you've never done that, it's just.
00:08:10 Interviewee 2 
OK, so for all VMS and physical server.
00:08:14 Interviewer
Yeah. Yeah. Well, I mean, the good thing about networks is the has VMS.
00:08:17 Interviewer
As well, yeah.
00:08:22 Interviewer
It would be quite interesting actually to do you think it would be worth knowing? For example, you in the server when you want to kind of, I don't know.
00:08:30 Interviewer
Would it be worth knowing what?
00:08:31 Interviewer
Hosts 1 certain VMS and stuff. Yeah, yeah, yeah. As in, like, I mean.
00:08:36 Interviewer
Yeah. What hosts?
00:08:43 Interviewer
So that that when the like the kind.
00:08:45 Interviewer
Of tasks it does, I guess, yeah.
00:08:47 Interviewee 2 
OK. And things like, you know, recent issues that machine, what's? Yeah. What's going on with right with yesterday, Michael?
00:08:59 Interviewee 2 
Graham Hunt reported his he couldn't mount his home at Linux home on 7.
00:09:09 Interviewee 2 
So that turned out being a.
00:09:12 Interviewee 2 
DNS configuration on 7.
00:09:15 Interviewee 2 
Was pointing at Folly. Folly is faulty and not functioning.
00:09:19 Interviewer
Also, I mean 7 faulty as well.
00:09:24 Interviewee 2 
Because for it it had 4/4 DNS entries all pointing at folly.
00:09:30 Interviewee 2 
It was a mistake. It was DNS 1DNS1DNS1 all pointing at folly. Instead of 1234 having the different.
00:09:33 Interviewer
Oh, awesome.
00:09:38 Interviewee 2 
DNS is.
00:09:42 Interviewee 2 
So because folly was faulty, he couldn't resolve anything.
00:09:46 Interviewer
Yeah. OK. So then that would be.
00:09:49 Interviewer
Yeah. So like say for example here so.
00:09:53 Interviewer
And I've I've searched for seven now. Yeah, and you can go into a journal. You can then add in like a.
00:09:59 Interviewer
Influence, success, boning or danger so.
00:10:02 Interviewer
It's weird that I have a. Suppose it, yeah.
00:10:06 Interviewer
And then you just specify the you know.
00:10:09 Interviewer
Config for the yeah.
00:10:12 Interviewee 2 
But yeah.
00:10:13 Interviewer
Yeah, I mean.
00:10:14 Interviewer
You know that that.
00:10:15 Interviewer
Kind of features are running in that box. Do you think it'd be worth kind of replicating the same thing?
00:10:20 Interviewer
Yeah, for instituting as well. So say for example, you're walking up, so you see someone's got, you know, say some serious samples and follies, got a red light or something. Yeah. You know that kind.
00:10:29 Interviewee 2 
Of thing, yeah.
00:10:35 Interviewer
Yeah, OK, cool.
00:10:42 Interviewer
Tracy said OK.
00:10:45 Interviewee 2 
Yeah, I mean, and that's also documenting.
00:10:47 Interviewee 2 
These issues that.
00:10:49 Interviewee 2 
You know, may reoccur. Yeah. And.
00:10:51 Interviewee 2 
You can just have a look at what's, yeah.
00:10:55 Interviewer
Yeah, OK, cool.
00:10:55 Interviewee 2 
And how it will solve?
00:11:00 Interviewer
I am.
00:11:01 Interviewer
I mean, do you have any other like kind of general suggestions for it? I mean, right now what I've got is very much networking and power, just information in general.
00:11:13 Interviewer
Did this ending even like a larger?
00:11:15 Interviewer
Scope. You can think of.
00:11:17 Interviewee 2 
Well, I mean you can, you can think about end of life, you know, yeah.
00:11:25 Interviewee 2 
And warranties information, stuff like that support information.
00:11:30 Interviewee 2 
For the servers, yeah.
00:11:32 Interviewer
Think why? Why? Very simple way of kind of doing that with cheating is I've I I was thinking of just if there's a a SharePoint link to it.
00:11:42 Interviewer
You know, just kind of linking to it and something like that cause it's documentation cause I think.
00:11:46 Interviewer
There's a few servers now with with links to, you know, their manuals and stuff. So, but also like if there's any kind of warranty information as well.
00:11:56 Interviewee 2 
And just to have that.
00:11:56 Interviewee 2 
As an alert, you know.
00:11:59 Interviewee 2 
OK. Yeah, 6 left or whatever, you know.
00:12:06 Interviewer
OK, cool.
00:12:09 Interviewer
OK.
00:12:09 Interviewee 2 
It might be a fact.
00:12:10 Interviewee 2 
That that server is going to be retired anyway, but you know, just listen up. It's good to know.
00:12:17 Interviewee 2 
OK.
00:12:19 Interviewee 2 
If you want to renew the.
00:12:22 Interviewee 2 
The warranty or support on that? Yeah, yeah.
00:12:26 Interviewer
OK. Yeah. Come look at that.
00:12:28 Interviewer
Yeah, that sounds good.
00:12:33 Interviewer
OK, if there's anything else.
00:12:37 Interviewer
OK, cool. Let me know. Obviously this is a very first thing, so I like to think that maybe.
00:12:45 Interviewer
My dad to show you an influence time or probably after Christmas now.
00:12:52 Interviewer
I kind of show you how it's working. So yeah. Then kind of go from there then so.
00:13:00 Interviewer
I've made some very kind of.
00:13:03 Interviewer
Crude crude, low fidelity.
00:13:15 Interviewer
So the the main features I'm kind of trying to do is obviously the adding, adding Connexions for Connexions update and interfaces and kind of information and stuff.
00:13:25 Interviewer
So kind of going back and locating devices and stuff, it'd be kind of narrow it down each way. You know, that kind of thing, you scan the cable.
00:13:35 Interviewer
You scan the device.
00:13:37 Interviewer
The cable type and then you choose side B as well. Yeah, the tab thing. So if I actually show you quickly cause I've kind of started doing development already, but don't tell Chris there.
00:13:49 Interviewer
We go so you can.
00:13:50 Interviewer
So you can kind of. So I've kind of improved upon it already by allowing you to.
00:13:56 Interviewer
So search for a device and set so I don't know closes.
00:14:06 Interviewer
OK.
00:14:08 Interviewer
Wait, maybe I need to log out.
00:14:12 Interviewer
Sorry, that's great demos.
00:14:26 Interviewer
There we go. So closes. Yeah. And then you can kind of then select it into the source. Hasn't got any because I'm putting in. So let's let's try see if.
00:14:33 Interviewee 2 
Yeah, yeah.
00:14:37 Interviewer
I don't know. It's two CF one and four up here, yeah.
00:14:41 Interviewer
The kind of interfaces.
00:14:43 Interviewer
And then you can swipe over and you choose. Then I don't know another one now.
00:14:48 Interviewer
It can be a.
00:14:49 Interviewer
Little bit tedious this aspect because you know it's it's very much swiping back to the floors and stuff.
00:14:54 Interviewer
There's lots of information kind of removing that again is to have us get a QR code and every single asset. So my idea is, is that in the end it's that.
00:15:08 Interviewer
For example, you want to add a connexion to something.
00:15:12 Interviewer
You scan a, you know you scan a, you scan cable and you scan B, and then everything's done. That's it. There's no, there's no need to do anything else. Kind of thing other than choosing interfaces.
00:15:24 Interviewer
So is that, you know, do you think that's probably better than what this kind of stage here?
00:15:30 Interviewer
You know, that kind of choosing a rack, choosing a device.
00:15:32 Interviewee 2 
Yeah, yeah, yeah, I think so. Yeah. OK.
00:15:39 Interviewer
And then viewing Connexions, then the idea is that once all the Connexions been added, all you need to do is scan the cable.
00:15:46 Interviewer
Yeah. You know or you can search for it manually again. So essentially when you scan the cable then it allows you to kind of see then a trace of what they do. So where they are on each device and stuff. So you can then.
00:16:03 Interviewer
So if I do it to the.
00:16:07 Interviewer
The newer 1, so that's the kind of view you'd end up having.
00:16:12 Interviewer
Is that you'd have two devices or more, because you can obviously trace them.
00:16:15 Interviewer
Back and stuff.
00:16:16 Interviewee 2 
Right.
00:16:16 Interviewer
Yeah. So say for example, if we do end up doing something like here, I don't end if end as the machine is dead or it's not.
00:16:23 Interviewer
Networking. Yeah, you can look at that port and then that port then will map back to to Commons room. And yeah, that device and.
00:16:32 Interviewer
Back down, that kind of thing.
00:16:34 Interviewer
But the the kind of information you're getting here is, is this kind of what you're on about earlier?
00:16:39 Interviewer
You know, it was that is added too much. Again, do you think?
00:16:41 Interviewee 2 
No, no, that's good. Yeah, yeah.
00:16:44 Interviewer
Mac address the address.
00:16:45 Interviewer
The primary one I imagine kind of thing.
00:16:49 Interviewer
Then you've got then your interface type so.
00:16:51 Interviewee 2 
Yeah, yeah.
00:16:52 Interviewer
Kind of quarter is.
00:16:53 Interviewer
And then the cable, then that would be like if that'll be like the label and then that would also then be the colour of the the cable as well.
00:16:57 Interviewee 2 
Yeah, yeah.
00:17:00 Interviewer
And if we were to do that at some point?
00:17:04 Interviewer
Yeah. So that kind of so rather than having like these kind of long.
00:17:09 Interviewer
You know, long picking of devices you can scan device say scan B and then you just pick the interfaces you know.
00:17:18 Interviewee 2 
Yeah, I mean.
00:17:18 Interviewee 2 
The colour coding is not for the cables.
00:17:21 Interviewer
Yeah, massive hell, yeah. Well, yeah, visually.
00:17:23 Interviewee 2 
It's just, yeah, yeah.
00:17:29 Interviewer
OK.
00:17:33 Interviewer
Yeah. Yeah. Well, yeah. I think the thing that's.
00:17:38 Interviewer
And then kind of then showing you can get that device interfaces as well. So if you want to look at CF104?
00:17:46 Interviewer
You can look through.
00:17:47 Interviewer
Each interface and nobody feel how it is or you know that kind of.
00:17:50 Interviewer
Thing as well.
00:17:51 Interviewee 2 
Yeah, yeah.
00:17:55 Interviewer
And again for devices.
00:17:57 Interviewer
So I kind of gone for this kind of.
00:17:59 Interviewer
Collapsible thing where rather than being shown all the information at once.
00:18:03 Interviewee 2 
Yes. Yeah.
00:18:04 Interviewer
You know, if you want the information, you can just choose that one.
00:18:09 Interviewer
Because if it's all kind of there, then you won't have to look anywhere for you. But then like so like you said with the with the, the historical thing almost having then like.
00:18:19 Interviewee 2 
You know the journal? Yeah.
00:18:23 Interviewer
You know well.
00:18:24 Interviewer
Back and fitness. Then you can have they can philtre them down by the history of that different changes and stuff.
00:18:30 Interviewer
Yeah. OK.
00:18:33 Interviewer
And all, like I said earlier.
00:18:36 Interviewer
Yeah. Yeah. So yeah. Do you have any kind of general comments on this as in, you know, anything at all?
00:18:45 Interviewee 2 
I mean, no, I mean that it just looks brilliant. That's exactly what I want, really. Because, I mean, I was saying about the the amount of information you get at.
00:18:50 Interviewer
Yeah, OK. Yeah.
00:18:56 Interviewee 2 
On just being able to see a specific focus.
00:19:00 Interviewee 2 
Detail on each machine is brilliant.
00:19:03
OK.
00:19:04 Interviewer
I mean, I mean, you know, you much information you get on one device can be or it's.
00:19:08 Interviewer
Just way too.
00:19:09 Interviewer
Yeah. And then just kind of hoping that we can maybe, yeah. OK.
00:19:19 Interviewee 2 
Is like.
00:19:22 Interviewee 2 
Pictorial representation of.
00:19:25 Interviewee 2 
Like an error on a a server you know like a a warning LED or something, yeah.
00:19:33 Interviewee 2 
So you would actually see the which led is, you know, physically on how it would look.
00:19:41 Interviewee 2 
OK, yeah, too much, but I know the bilos give.
00:19:48 Interviewee 2 
Sort of gooey representations of like.
00:19:50 Interviewee 2 
A of a J bolt.
00:19:53 Interviewee 2 
And you can actually see which disc is flashing and that kind.
00:19:55 Interviewer
Yeah, OK. No warnings so kind.
00:19:58 Interviewer
Of based on the devices.
00:20:01 Interviewer
So you know if if there's. Yeah. OK.
00:20:05 Interviewer
Yeah. So.
00:20:07 Interviewer
One of the kind of stretch goals of this that Chris suggested was AR. Yeah. Yeah. Mentioned. Yeah. And whether, you know, whether that's thing I'm I'm able to do within the the scope of this, the, the the station itself.
00:20:22 Interviewer
Whether afterwards, yeah, something added to it.
00:20:25 Interviewer
A kind of.
00:20:26 Interviewer
Like a a way of you know, if I if every for every single.
00:20:29 Interviewer
Device tab we've got.
00:20:30 Interviewer
You kind of map the front and the back. You've got the LED's and that kind of thing and what each light might mean and yeah, yeah.
00:20:33 Interviewee 2 
Yeah, yeah.
00:20:37 Interviewer
It might take a very long time to kind of document it all, but once you've.
00:20:40 Interviewer
Got it. Then it's kind of.
00:20:44 Interviewer
So you know.
00:20:46 Interviewer
So the idea would be using the QR codes as like a a marker. So it scans the QR code that picks up the device and stuff and you're able to kind of map the front of it.
00:20:55 Interviewer
So if it's a switch, for example, click on it.
00:20:58 Interviewer
And a port one.
00:20:59 Interviewer
And clicks and port one. If it's connected, it brings up another little.
00:21:02 Interviewer
Box that says where it goes to one VLAN.
00:21:05 Interviewer
It is that kind of thing.
00:21:06 Interviewer
Where where it goes to that.
00:21:08
You know.
00:21:10 Interviewer
Yeah. Yeah. OK.
00:21:14 Interviewer
Well, that's very.
00:21:16 Interviewer
You know, I think.
00:21:18 Interviewer
If, if, if.
00:21:18 Interviewer
We, if I could have dive down one kind of rabbit hole of the that kind of feature and then miss out all the basic ones. You know, like you said, like this, it needs to have like we need to get the information, call information down first rather than kind of jumping down to. Yeah, you know. So I think that's probably what I'll I'll make. I'll just do.
00:21:36 Interviewer
Is there's a?
00:21:37 Interviewer
Let's call to it first.
00:21:38 Interviewer
OK, cool.
00:21:42
OK.
00:21:44 Interviewer
So there's three different.
00:21:48 Interviewer
Things I want to show you. So one is called net sunbird.
00:21:52 Interviewer
Which is like a like a fully fledged solution. So this is like 10 grand a year, kind of that kind of.
00:22:01 Interviewer
So they have this kind of mapping.
00:22:04 Interviewer
You know of like the server room and stuff now.
00:22:09 Interviewer
It's like it's quite an idealistic thing, isn't it? But also then.
00:22:14 Interviewer
You know, where do you think? Like a an like an AR similar thing like.
00:22:18 Interviewer
This would be.
00:22:20 Interviewer
Do you think you?
00:22:20 Interviewer
Ever use it?
00:22:26 Interviewee 2 
Yeah, I mean the.
00:22:32 Interviewee 2 
Yes, I would, I mean.
00:22:35 Interviewee 2 
It's it's difficult if you've got.
00:22:38 Interviewee 2 
A server room down the hallway.
00:22:41 Interviewee 2 
Yeah, and not actually.
00:22:50 Interviewee 2 
But yeah, I mean.
00:22:55 Interviewee 2 
It would be ideal, but how?
00:22:58 Interviewee 2 
I don't know if you need.
00:23:00 Interviewee 2 
That much information or to spend that much on it to get the information that you need, yeah.
00:23:09 Interviewer
So maybe I mean.
00:23:13 Interviewee 2 
I mean, that's great. If you could say yes, you can spend that much money, then yeah, it would be brilliant.
00:23:18 Interviewee 2 
To have that.
00:23:19 Interviewer
Yeah, exactly. Yeah. This was just like the.
00:23:26 Interviewer
Like the limitations of lots of things you know, is it like you said financially that if you can drop that kind of money into this kind of thing?
00:23:35 Interviewer
Yeah, like you can even you can zoom in and you.
00:23:37 Interviewer
Can like look at.
00:23:38 Interviewee 2 
Yeah, I mean, it's brilliant. Yeah, yeah.
00:23:43 Interviewer
So you know whether.
00:23:47 Interviewer
You know.
00:23:47 Interviewer
You know, this is not my skill set.
00:23:51 Interviewer
You know, like nothing but, you know, like this kind of thing.
00:23:54 Interviewer
I mean, it's good to kind of note down that this is you know like you can some parts of it not very.
00:23:59 Interviewer
Fun to navigate.
00:23:59 Interviewer
With but like this kind of like these.
00:24:02 Interviewer
Kind of draw.
00:24:05 Interviewer
These kind of like these.
00:24:07 Interviewer
Kind of drawings and funny stuff.
00:24:09 Interviewer
That that can be.
00:24:10 Interviewer
Probably done with that. You're able then to kind of look at then.
00:24:11 Interviewee 2 
Yeah, yes, yeah.
00:24:17 Interviewer
I don't know what's what's connected.
00:24:19 Interviewer
This one is disconnected.
00:24:23 Interviewer
You just kind of get like a.
00:24:25 Interviewer
An overview as well. Yeah. No. See, these are for very well. This is the data centres. Yeah, we've got we've got maybe we've got like one row there and we.
00:24:37 Interviewer
So I think that's that's one thing. That's one thing I've noticed a lot of looking when I was looking into that box and stuff is.
00:24:44 Interviewer
There's no kind of solution for like our kind of size. Usually they are. It's either nothing or you get this massive piece of software like I think this.
00:24:53 Interviewer
Has got like like where the tracking is or something.
00:24:58 Interviewer
You can like try like cheque like a the weather map and.
00:25:02 Interviewer
And it's just like.
00:25:05 Interviewer
You know you you probably needed quite a bit of training.
00:25:08 Interviewer
In this you know.
00:25:11 Interviewer
So similar to, yeah, I mean, you know like.
00:25:16 Interviewer
He went to go point earlier.
00:25:18 Interviewer
You know.
00:25:20 Interviewer
Having like a A.
00:25:21 Interviewer
Nice overview of something as well.
00:25:25 Interviewer
You know, like having like a, like a focus of of information.
00:25:28 Interviewee 2 
Yeah, yeah.
00:25:30 Interviewer
So something like this could be once we are able to.
00:25:32 Interviewer
Collect this kind of information.
00:25:34 Interviewer
Then it would be quite interesting to see.
00:25:38 Interviewee 2 
What, just for the effects on the data centre itself and the weather conditions?
00:25:41 Interviewer
Yeah. Yeah. Well, you know what? They it doesn't really affect us so much.
00:25:46 Interviewee 2 
One one thing that's been noticed quite interesting about the.
00:25:51 Interviewee 2 
Temperature monitoring. C36 is how stable it's been recently.
00:25:59 Interviewee 2 
And I think that's just because the sun hasn't been out.
00:26:04 Interviewee 2 
Because there's windows there, yeah.
00:26:07
UM.
00:26:09 Interviewee 2 
And obviously if you've.
00:26:10 Interviewee 2 
Got windows and server which you shouldn't have. Anyway I think that's been you know, you can either you can correlate it with the sun coming through the window.
00:26:20 Interviewee 2 
There and that and.
00:26:21 Interviewee 2 
The the sort of the peaks and the.
00:26:24 Interviewee 2 
I just thought about it the other day.
00:26:26 Interviewee 2 
I thought why is it suddenly gone very stable?
00:26:29 Interviewee 2 
But it's been cloudy for the last three days, so.
00:26:36 Interviewer
For now.
00:26:39 Interviewer
It's probably even out there, isn't it? Like it's a couple of spikes, yeah.
00:26:45 Interviewer
It's very impressive. It's able to hold a very.
00:26:48 Interviewer
Such a consistent temperature I was expecting like kind of this to be the kind of.
00:26:54 Interviewer
You know, this kind of fluctuation. Yeah. But the fact that it stays between.
00:26:59 Interviewer
You know 19 Celsius is, is is the so.
00:27:04 Interviewer
Maybe. Maybe the senses fail.
00:27:11 Interviewee 2 
I think, yeah.
00:27:13 Interviewee 2 
I mean, it does make a massive difference with those windows in there.
00:27:16 Interviewer
Yeah. Yeah. Well, yeah.
00:27:17 Interviewee 2 
As you'd expect.
00:27:18 Interviewer
When to think it spiked up to? Well, obviously it was like.
00:27:22 Interviewer
40 yeah, during.
00:27:23 Interviewer
The the heat wave at the end there.
00:27:32 Interviewer
Yeah, like, yeah, we're talking like the last.
00:27:34 Interviewer
Like 2 weeks or so, it's very much.
00:27:41 Interviewer
OK, OK.
00:27:48 Interviewer
Should you have like kind of you know doing?
00:27:52 Interviewer
Do you have any kind of an observation to this? In general? You know, if you think about?
00:27:56 Interviewer
Compared to that box, you know.
00:28:10 Interviewee 2 
I mean that to me the net box is.
00:28:14 Interviewee 2 
It's easier to use and visually, yeah.
00:28:17 Interviewee 2 
I think there's too much there.
00:28:20 Interviewer
Yeah, I.
00:28:23 Interviewer
It was interesting. One first.
00:28:25 Interviewee 2 
It's just a matter of, well, obviously you'd get to to know it once you've used it a few times, you find out, but.
00:28:35 Interviewee 2 
Yeah, it's that matter of of having.
00:28:37 Interviewee 2 
Too much stuff.
00:28:40 Interviewee 2 
Available, yes, yeah.
00:28:41 Interviewee 2 
Yeah, but maybe that's just me, but.
00:28:44 Interviewee 2 
You know, everybody's different anyway, but yeah.
00:28:46 Interviewer
I think really just like I don't really need to know, you know, because these kind of assets, they're all, they're all, everything's listed under one thing says 300 assets listed here and you've got like.
00:29:02 Interviewer
Like the.
00:29:05 Interviewer
Not like this is. This is just endless, yeah.
00:29:09 Interviewer
And well.
00:29:10 Interviewee 2 
Yeah, I mean, that's why.
00:29:11 Interviewee 2 
You could argue that the AR thing is.
00:29:16 Interviewee 2 
Is almost the best.
00:29:19 Interviewee 2 
Because you've got a mental picture of of the plan of.
00:29:24 Interviewee 2 
Be 51 in your head.
00:29:25 Interviewer
Yeah, yeah.
00:29:26 Interviewee 2 
And to actually be able to see it physically and you know well, Colossus is there.
00:29:31 Interviewee 2 
Focus. Yeah, on that.
00:29:33 Interviewee 2 
And get the information I need from that, yeah.
00:29:35 Interviewer
Well, like while.
00:29:35 Interviewer
You're in situ as well, yeah, yeah.
00:29:41 Interviewer
OK.
00:29:43 Interviewer
Too much information.
00:29:49 Interviewee 2 
Yeah, and a visual representation I think is is the way to go. What for me would be anyway, just.
00:29:59 Interviewee 2 
Because it's it's easier to relate to.
00:30:02 Interviewer
Yeah, rather than needing to kind of.
00:30:06 Interviewer
Yeah, like, yeah, visual one. I I I'm very much a visual person. You know, if I can see that kind of connexion, I don't seem tend to make them based on this data.
00:30:17 Interviewer
OK. I mean, you know, I'll so the next thing is I'll show you snap box. I mean obviously you know you you've, you've interacted with it you know so this is like a the demo, yeah, so this is kind of like get used fully. So you can kind of see like how it feeds and stuff.
00:30:36 Interviewer
And you know that's that's saying that's.
00:30:39 Interviewer
We aim to our dinner as well.
00:30:41 Interviewee 2 
Yes. Yeah.
00:30:44 Interviewee 2 
And the redundant power supplies and yeah.
00:30:46 Interviewer
Yeah, I was poisoned. And I think then you can even think based on like a rap. So I don't like it.
00:30:55 Interviewer
Just close it, you can.
00:30:57
Good power in here.
00:30:59 Interviewer
Yeah, you can get like power utilisation and stuff. Yeah, so.
00:31:03 Interviewer
Obviously cause we've got like cross.
00:31:06 Interviewer
Cable tracks and stuff. It has to be based on the the PDU, the the actual distribution board.
00:31:12 Interviewer
Michael had a good idea of labelling each one of the kind of switches to what devices they power, because you can actually you can route it down to that kind of level is that if you.
00:31:25 Interviewer
Look at you.
00:31:26 Interviewer
Know this switch? Here you can see that powers closest Xavier.
00:31:32 Interviewer
But that kind of thing. No. Yeah. So I think the the main thing is adding on to netbox and kind of replacing the things that are complicated about it or tedious because I think 11, I was reading before the one of the biggest problems with like documentation jams that people don't want to do it if it's going to take them.
00:31:33 Interviewee 2 
Yeah, yeah.
00:31:51 Interviewer
Too long. It's tedious to do.
00:31:53 Interviewer
And I think if.
00:31:53 Interviewer
I can kind of replace the.
00:31:55 Interviewer
The the the boarding pass from it all. Like say for example like the.
00:32:03 Interviewer
Like adding it adding Connectional Networks is a pain.
00:32:05 Interviewer
In the ****.
00:32:07 Interviewer
Because you have to go through the device.
00:32:10 Interviewer
That's good.
00:32:13 Interviewer
To go to a named device, for example, go to the front port. Then you have to then go, then to.
00:32:24 Interviewer
OK.
00:32:27 Interviewer
You might have to go into the port there. There we go, click on the port and then you connect then to.
00:32:32 Interviewer
An interface and then then you select. Then you know, say for example another device then here.
00:32:38 Interviewer
And you can specify all the cables and the types and all that. Kind of. Yeah, yeah. Whereas.
00:32:44 Interviewer
With this, and would literally be be scams. Are they and you slapped the water is and you have been kind of cable and then it knows all the.
00:32:51 Interviewer
Right. Information for you. Yeah, yeah.
00:32:54 Interviewer
So then that's some kind of.
00:32:55 Interviewer
Meaning with it all.
00:32:58 Interviewer
But like like you said earlier as well, with the virtual machines and stuff, we've got all of our virtual machines now on.
00:33:04 Interviewee 2 
On here, yeah.
00:33:07 Interviewer
You know, so you then you kind of know then so.
00:33:13 Interviewer
Why is Keith?
00:33:14 Interviewer
'S got 2 terabytes.
00:33:18 Interviewee 2 
So that isn't an old mral server client server.
00:33:25 Interviewee 2 
I think probably only Chris is using.
00:33:34 Interviewer
You didn't tell me that.
00:33:34 Interviewee 2 
Yeah, that's that's the W server.
00:33:38 Interviewer
OK.
00:33:41
Look at this.
00:33:47 Interviewer
Just see, but yeah, you've got you've got all the.
00:33:50 Interviewer
Let's click on Tom, for example.
00:33:55 Interviewer
I've managed to kind of get some information from there as well, so like this IP address is Vlans.
00:33:58 Interviewee 2 
Yeah, yeah, yeah.
00:33:59 Interviewer
And that kind of thing, but also then if you?
00:34:02 Interviewer
Look at.
00:34:03 Interviewer
You can look at the cluster and each of the clusters there will have to look at the cluster.
00:34:14 Interviewer
Like just circles.
00:34:17 Interviewer
I'm being silly here.
00:34:24 Interviewer
So if you're in the cluster, yeah, you can see, then you should be able to see the.
00:34:26 Interviewee 2 
All right.
00:34:31 Interviewer
There you go. So that all the virtual machines. Yeah, the devices that they have. So these are then the actual.
00:34:37 Interviewer
The posts themselves.
00:34:38 Interviewee 2 
Yes. Yeah, excellent, yeah.
00:34:38 Interviewer
They could have LinkedIn.
00:34:41 Interviewer
The link them back then so then.
00:34:44 Interviewer
So this is all the things in honesty. And then think then we could do then is we go to.
00:34:53 Interviewer
You can then find.
00:35:01 Interviewer
See it's.
00:35:03 Interviewer
Virtual machines.
00:35:18 Interviewer
I think.
00:35:24 Interviewer
Yeah, but yeah, that kind of.
00:35:28 Interviewer
Kind of.
00:35:29 Interviewer
Getting all this information and compare.
00:35:30 Interviewer
The important stuff to pile down, OK?
00:35:34 Interviewee 2 
Yeah, that's that was really good. OK.
00:35:39 Interviewer
So do you have any comments on that book in general?
00:35:48 Interviewee 2 
I I like it visually actually.
00:35:51 Interviewee 2 
The way it's arranged, yeah.
00:36:05 Interviewee 2 
And I think there's.
00:36:06 Interviewee 2 
You know from from what I've seen, there's.
00:36:09 Interviewee 2 
You could get.
00:36:11 Interviewee 2 
Anything any information you want. Really. Yeah. From there.
00:36:18 Interviewer
Feature Rich the last day.
00:36:19 Interviewee 2 
Yes, yes, it's a rich, yeah.
00:36:27 Interviewer
Yeah, like, you know, like he was saying.
00:36:29 Interviewer
With Michael earlier about having.
00:36:31 Interviewer
Been able to kind of get all the information you've got from on the floor panels. Mm-hmm. Then, because you can do that for essentially everything.
00:36:37 Interviewer
Really. Yeah, you can add multiple rooms and stuff. So like slide. So comp site and then each one then would have locations. So in our case, we've got only three locations. So you'd be able to add then.
00:36:52 Interviewer
You know, like a A room.
00:36:56 Interviewee 2 
Tenant. So that could be that kind of thing. Yeah. I mean having that only one place. Yeah, is great.
00:37:04 Interviewer
Yeah, I think that's, I think that's the key. You know, my aim with it was kind of have it in one place in a nice.
00:37:12 Interviewer
Homogeneous form, yeah.
00:37:14 Interviewee 2 
And the fact that you can.
00:37:15 Interviewee 2 
Do that with that.
00:37:18 Interviewer
Yeah, yeah.
00:37:20 Interviewer
OK. On a final note then I'll show you the only app.
00:37:24 Interviewer
I could find which is.
00:37:26 Interviewer
Similar similar to what I'm kind of able to do, it's called Pathfinder.
00:37:37 Interviewer
Yeah, it's a companion to like the full, almost very simple. So I'll be doing really it's a companion to Pathfinder, which is like a similar to some.
00:37:46 Interviewee 2 
Bird thing, right?
00:37:47 Interviewer
And it kind of works on the information and stuff where it it allows you to send like tasks from the desktop version to the mobile. So say for example.
00:37:57 Interviewer
You were in the office somewhere else and there was a technician in a in a data centre. Some way you could send to their device to do a switch off.
00:38:07 Interviewer
Switch 4. Two. Yeah, yeah, but it uses, like, this hierarchical view that Michael quite like it allows you to kind of philtre down. So you've got your location.
00:38:18 Interviewee 2 
Yeah, yeah.
00:38:20 Interviewer
You've got your buildings.
00:38:21 Interviewer
So I don't know. It's good to.
00:38:25 Interviewer
Let's go to the data centre and then.
00:38:28 Interviewer
Floor 3.
00:38:30 Interviewee 2 
Really good. Yeah.
00:38:32 Interviewer
In different rooms, some numbers and stuff, and then you can kind of just go to have three or three.
00:38:38 Interviewer
And then you've got then yeah.
00:38:40 Interviewer
You know you've got your your devices done. Yeah. Now that's kind of I've only.
00:38:44 Interviewer
Kind of thought about today.
00:38:45 Interviewer
Really. But I mean, do you kind of?
00:38:48 Interviewer
Like that hierarchical view food or yeah.
00:38:49 Interviewee 2 
I do. That's really good, yeah.
00:38:52 Interviewee 2 
Who's in that room? Yeah, well, you're exactly. No.
00:38:58 Interviewer
Information, yeah.
00:39:04 Interviewer
Like a map of the PC, I think. OK, what's the point of that? But yeah, I mean, being able to maybe could integrate that with snipe, yeah, and kind of.
00:39:16 Interviewer
Throw all together.
00:39:17 Interviewee 2 
Brilliant. Yeah. Really, really good and.
00:39:24 Interviewee 2 
I mean, just support wise knowing.
00:39:28 Interviewee 2 
Yeah, knowing all that information beforehand is just brilliant.
00:39:43 Interviewee 2 
Diagnose it without a visit. Yeah, yeah.
00:39:45 Interviewer
Well, well, you know.
00:39:49 Interviewer
If you look.
00:39:49 Interviewer
At, if you look at, you know this this PC here and see what what's plugged into.
00:39:55 Interviewer
Then you can then go back to. There you go. So there we go. That's that's the kind of tracing. Yeah. Yeah. So you've kind of got. That's the PC.
00:40:04 Interviewer
That then goes into that patch panel.
00:40:07 Interviewer
That then links into this switch. Yeah. You know, that kind of thing. And you've got each kind of cable.
00:40:12 Interviewer
Labelled the type.
00:40:12 Interviewer
And you know, and you've kind of got this this full.
00:40:15 Interviewer
Mapping. Yeah, and.
00:40:20 Interviewee 2 
I mean, just knowing what DHCP and DNS servers are using that PC.
00:40:28 Interviewer
Yeah, I mean, you know, I think when you're in, when you're in situate stuff, if you're able to kind of assign.
00:40:33 Interviewer
So you select the room and stuff like that. You can add, you know, a new. Yeah. OK, because just.
00:40:45 Interviewee 2 
Yeah, I mean the the app could almost.
00:40:51 Interviewee 2 
Tell you what was going wrong and if it's DNS DHCP issue.
00:41:04 Interviewer
Yeah, yeah.
00:41:06 Interviewer
Yeah. OK, yeah, I think.
00:41:08 Interviewer
That's actually a really cool thing to do, is being able to.
00:41:12 Interviewer
Quite helpful, you've.
00:41:13 Interviewer
Kind of already mapped all the floor panels.
00:41:15 Interviewer
Because I can just kind of.
00:41:19 Interviewer
Move in to.
00:41:19 Interviewer
Watch the place to another and then.
00:41:22 Interviewer
OK.
00:41:24 Interviewer
And Michael said early about it's good thing to say. For example, when Elena needs to.
00:41:29 Interviewer
You know, if someone else is moving into an office and stuff and you know that if it's a four pile is working or or not working, that kind of thing, but I.
00:41:36 Interviewee 2 
Mean that's one of the things that.
00:41:39 Interviewee 2 
You know I've I've had in the past that.
00:41:43 Interviewee 2 
He's doing an inventory and people do move rooms without telling you. Yeah. And you find out that that PC is no longer in that room.
00:41:56 Interviewee 2 
It's been plugged into the network port in, you know, a room for for, you know, down in the next floor. So you know.
00:42:05 Interviewer
I think that's the that's the problem is that data like this kind of information changes very quickly.
00:42:11 Interviewer
No, they did, you know, yeah.
00:42:15 Interviewer
But I suppose then having a history of it as well is not a bad thing either. Yeah, if you get to a point where it's all been done and then just updating over time, then isn't incremental.
00:42:23 Interviewee 2 
This PC has actually moved.
00:42:25 Interviewee 2 
From C-83 to C, Yeah, 87. Yeah. OK.
00:42:27 Interviewer
Whatever, yeah.
00:42:31 Interviewer
Very good. So you could.
00:42:35 Interviewer
The the set types, that's that you use is.
00:42:40 Interviewer
As part of that.
00:42:40 Interviewer
As well. So rather than needing to get new.
00:42:43 Interviewer
Labels and stuff. If every PC's got some nice.
00:42:45 Interviewee 2 
Well, yeah. Also if that PC is plugged into data point up there, that Mac address has now moved. Yeah, yeah.
00:42:55 Interviewer
OK.
00:42:55
Sounds very good.
00:42:58 Interviewer
Would there be a way of being able to?
00:43:01 Interviewer
Ping, but go look, look down every single patch like a floor port and Nolan. Yeah. I mean, William had all that information initially.
00:43:10 Interviewee 2 
Before all the.
00:43:12 Interviewee 2 
Walls in the moved and floor boxes moved and.
00:43:17 Interviewee 2 
He actually had, you know, he could philtre it down to Mac, Mac address and the data point.
00:43:25 Interviewee 2 
Per switch.
00:43:26 Interviewer
Oh wow.
00:43:27 Interviewer
OK.
00:43:31 Interviewee 2 
So I mean I presume.
00:43:32 Interviewee 2 
You can do that now, yeah.
00:43:36 Interviewee 2 
With an accurate map of everything now where that data points are and yeah.
00:43:47 Interviewer
I like the idea of having it. Kind of.
00:43:49 Interviewer
Because I was very be 51, you know networking. Except we'll be able to extend out to everything else. I think that's not just the only part of it. Yeah. OK, cool.
00:44:00 Interviewer
I mean, I mean that's pretty much done now. So do you have any other kind of you know comments and?
00:44:07 Interviewee 2 
No, it's.
00:44:09 Interviewer
Very useful. Yeah. Well, yeah.
00:44:11 Interviewee 2 
Actually, it seems that she came as well.
00:44:13 Interviewee 2 
But it's yeah.
