\subsection{Observation 1}
\label {sec:UserObservation1}
\begin{enumerate}
    \item Automatic focus of keyboard on dropdown search menus.
    \item Bug found with filtering by location on connection search page.
    \item Arrow directions of location hierarchy are confusing.
    \item Expandable Lists for Racks with devices nested inside them.
    \item Keep last item selected in hierarchy when navigating back.
    \item Add more home screen buttons for quick access to common pages.
    \item Change the side menu icon to a gear icon to indicate settings.
    \item Bug with loading in interfaces on modify connection page.
    \item Add a hint to modify connection to suggest scanning for device or entering ID to start.
    \item Add more labels to text fields to make it easier to understand what they are for.
    \item Rename the "New Search" button to "back" and navigate one up the tree. 
    \item For interfaces that don't have a connection on them, automatically navigate the user to the Add Connection page on click.
    \item Bug on add connection page where an error causes a white screen rather than error message.
    \item Don't allow the user to select an interface that is already connected.
    \item Make missing fields on the add connection page more obvious - red text or highlight.
\end{itemize}

\subsection{Observation 2}
\label {sec:UserObservation2}
\begin{enumerate}
    \item The home button on the interface display isn't clear. 
    \item What interfaces the cable is connected to is not clear.
    \item Button to go from hierarchy to the device itself. 
    \item Loading interfaces indication on add and modify connection.
    \item Further work suggestion to integrate the new connection addition to a printing system.
\end{enumerate}
